Figures

### 2018-04-02 scripts/analysis.Rmd
more expo plots, show corr matrix as heatmap
heatmap adjustments

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6, fig.pos = 'H')
```

@@

```{r cor_mat_table, echo=FALSE, results='asis'}

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
```

@@

```{r cor_mat_hmap, echo=FALSE, warning=FALSE, out.width="3.5in", fig.cap="Connectivity metric correlation heatmap.", message=FALSE}

@@

```{r graphical_exploratory_analysis_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=8.4, fig.cap="Exploratory plots cont"}
